### 2023-07-28 xFitter/PDF_profiling/PDF4LHC21/statOnly/collectPlots.tex
Updating all xFitter files/directories

FASERv2\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}

@@

FASERv2 nochargediscrimination\\
\newcommand{\dataset}{_nochargediscrimination}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}

@@

FASERv2 inclusive\\
\renewcommand{\dataset}{_inclusive}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}

@@

FASERv2 inclusive nochargediscrimination\\
\renewcommand{\dataset}{_inclusive_nochargediscrimination}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}

@@

FASERv2 charm\\
\renewcommand{\dataset}{_charm}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}

@@

FASERv2 charm nochargediscrimination\\
\renewcommand{\dataset}{_charm_nochargediscrimination}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}

>>>>

FASERv2\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}

@@

FASERv2 nochargediscrimination\\
\newcommand{\dataset}{_nochargediscrimination}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}

@@

FASERv2 inclusive\\
\renewcommand{\dataset}{_inclusive}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}

@@

FASERv2 inclusive nochargediscrimination\\
\renewcommand{\dataset}{_inclusive_nochargediscrimination}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}

@@

FASERv2 charm\\
\renewcommand{\dataset}{_charm}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}

@@

FASERv2 charm nochargediscrimination\\
\renewcommand{\dataset}{_charm_nochargediscrimination}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}

FASERv\\
\renewcommand{\experiment}{FASERv}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}

SND\\
\renewcommand{\experiment}{SND}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}

### 2023-07-28 xFitter/PDF_profiling/PDF4LHC21/systVar05/collectPlots.tex
Adding results corresponding to stat-only and all-syst-unc-uncorrelated cases
Updating all xFitter files/directories

\newcommand{\figw}{70mm}
\newcommand{\experiment}{FASERv2}
\newcommand{\unctype}{statOnly}

@@

FASERv2 charm nochargediscrimination\\
\renewcommand{\dataset}{_charm_nochargediscrimination}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}

>>>>

\newcommand{\figw}{70mm}
\newcommand{\experiment}{FASERv2}
\newcommand{\unctype}{systVar05}

@@

FASERv2 charm nochargediscrimination\\
\renewcommand{\dataset}{_charm_nochargediscrimination}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}

FASERv\\
\renewcommand{\experiment}{FASERv}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}
